---
title: "data_dictionary"
author: "Aoi, Jillian, Ester"
date: "4/15/2018"
output: html_document
---

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(mosaic)
```


```{r}

# Calls from the url, doesn't need a computer pathway
oscars <- read.csv("https://raw.githubusercontent.com/BuzzFeedNews/2018-03-oscars-script-diversity-analysis/master/data/actor-metrics.csv")

words <- read.csv("https://raw.githubusercontent.com/BuzzFeedNews/2018-03-oscars-script-diversity-analysis/master/data/character-word-counts.csv")


# #can't import need to solve, rename it to "group-D-data.csv"
# actor-metrics <- read_csv("/Users/aoiogawa/SDS_201_final_project/data/actor-metrics.csv")
# View(actor_metrics)

# main characters
main_character <- oscars %>%
  filter(words >= 1000)

favstats(main_character$words)

# sub characters
sub_character <- oscars %>%
  filter(words < 1000)

favstats(sub_character$words)

#actress
actress <- oscars %>%
  filter(gender == "female")

favstats(actress$words)

# main female actor 
main_actress <- actress %>%
  filter(words >= 1000)

favstats(main_actress$words)

# actors who are poc
poc_actor <- oscars %>%
  filter (race_simple == "POC") 

favstats(poc_actor$words)

#main character actors who are poc 
main_poc_actor <- main_character %>%
  filter (race_simple == "POC") 

favstats(main_poc_actor$words)

#sub character actors who are poc 
sub_poc_actor <- sub_character %>%
  filter(race_simple == "POC")

favstats(sub_poc_actor$words)

# main white actor 
main_white_actor <- oscars %>% 
  filter(race_simple == "White") %>%
  filter(words >= 1000)

# sub white actor 
sub_white_actor <- oscars %>%  
  filter(race_simple == "White") %>%
  filter(words < 1000)

oscars %>% 
  filter(race == "Asian")

tally(race_simple ~ gender, oscars)  
tally(race ~ gender, oscars)

# number of characters per movie
n_characters <- oscars %>% 
  group_by(year, film) %>%
  summarise(n_characters = sum(n_distinct(characters)))

# words per movie
words_per_movie <- oscars %>%
  group_by(year, film) %>% 
  summarise(sum_words = sum(words))

```


We decided that in order to distinguish main characters from supporting characters, that we would measure an actor's importance based on their world count. We arbitrarily decided that we would use 1000 words as the amount that set an actor apart as a main character. However, not all main characters speak many words, or even at all. For example, the main character in the 2017 film "Shape of Water" is a mute woman, who does not speak any words. Since Sally Hawkins, the actress that plays the mute woman, is not even mentioned in this data set, we can assume that the compilers of this data decided that characters with no spoken words were not of note. Because of this, our data set excludes characters from films where the main characters do not speak any words, and discriminates against those who do not speak many words.
